---
title: "DATA_605_Assignment_12"
author: "Md Jalal Uddin"
date: "November 13, 2016"
output: html_document
---

Problem:Using the stats and boot libraries in R perform a cross-validation experiment to observe the bias variance tradeoff. You'll use the auto data set from previous assignments. This dataset has 392 observations across 5 variables. We want to fit a polynomial model of
various degrees using the glm function in R and then measure the cross validation error
using cv.glm function. Fit various polynomial models to compute mpg as a function of the other four variables acceleration, weight, horsepower, and displacement using glm function.
will fit a 2nd degree polynomial function between mpg and the remaining 4 variables and
perform 5 iterations of cross-validations.

Solution:

```{r}
#Load packages stats, boot, and dplyr
library(stats)
library(boot)
library(dplyr)

```


```{r}
#read auto-mpg data using read.csv and name the variable using names function. 

auto_mpg_data2 <- read.csv("C:/Users/sql_ent_svc/Desktop/MSDA Assignment/DATA_605/Assignment_11/auto-mpg.data", sep = "", header = FALSE)

names(auto_mpg_data2) = c("mpg", "displacement", "horsepower", "weight", "acceleration")

```


```{r}
# fit a polynomial model of auto-mpg data using glm function. 
glm.fit = glm(mpg ~ poly(displacement + horsepower + weight + acceleration, 2), data = auto_mpg_data2)

# fit a polynomial model of degree 1 to 8 using glm function.Here we fit 2nd degree polynomial function between mpg and other variables. We performed here 5 iteration with cross-validation. 

degree = 1:8
cv.err5 = c()

for(i in degree) {
  glm.fit = glm(mpg ~ poly(displacement + horsepower + weight + acceleration, i), data = auto_mpg_data2)
  cv.err5 = c(cv.err5, cv.glm(auto_mpg_data2, glm.fit, K = 5)$delta[1])
}

```

Problem: Once you have fit the various polynomials from degree 1 to 8, you can plot the crossvalidation error function

Solution:

```{r}
#fit crossvalidation error function with degree 1 to 8
plot(degree, cv.err5, type = 'b')

```

```{r}
# Now, I will test with larger degree. Fitting a polynomial model of degree 1 to 17 using glm function and finally fitting crossvalidation error function of this polynomial model. 

degree = 1:17
cv.err5 = c()

for(i in degree) {
  glm.fit = glm(mpg ~ poly(displacement + horsepower + weight + acceleration, i), data = auto_mpg_data2)
  cv.err5 = c(cv.err5, cv.glm(auto_mpg_data2, glm.fit, K = 5)$delta[1])
}


plot(degree, cv.err5, type = 'b')


# Conclusion: For 1 to 8 degrees of polynomial model I get U shaped crossvalidation error function but for larger degrees of polynomial model, I get such crossvalidation error function in which error scored have wide variance.   

```

